---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# cranq

(Pronounced either like "cran queue" or "crank", I don't mind.)


The goal of cranq is to provide a quick way to check the status of packages in
CRAN's incoming package queue.

This can be especially useful if you're releasing a package and want to 
check on the status of your submission.

## Installation

You can install the development version of cranq like this:

``` r
remotes::install_github("sellorm/cranq")
```

## Usage

There are basically two things cranq can do for you. You can view the incoming
queue or you can search for a package within the queue.

To show all packages in the incoming queue:

```{r}
library(cranq)
incoming()
```

To show a specific incoming stage by name:

```{r}
incoming("newbies")
```

To find a specific package within all the queues:

```{r}
check_package("musclesyneRgies")
```

Edgar Ruiz and Hadley Wickham performed some
[analysis of what these stages might mean](https://github.com/edgararuiz-zz/cran-stages).

## License

Released under the [MIT License](LICENSE.md).

Copyright (c) 2022 Mark Sellors.
