---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# cranq

(Pronounced either like "cran queue" or "crank", I don't mind.)


The goal of cranq is to provide a quick way to check the status of packages in
CRAN's incoming package queue.

This can be especially useful if you're releasing a package and want to 
check on the status of your submission.

Having said that, most people will be better off using the
[R-Hub CRAN Incoming Dashboard](https://r-hub.github.io/cransays/articles/dashboard.html)
instead of this package.

## Installation

You can install the development version of cranq like this:

``` r
remotes::install_github("sellorm/cranq")
```

## A quick note on usage

This package scrapes the web pages for the
[CRAN incoming queue](https://cran.r-project.org/incoming/)
and as such relies on the fact that this is easily available, public information.

Those pages exist at the discretion of the CRAN team.
They're a privilege, not a right.
So just like you wouldn't load up all those pages in your web browser and keep
mashing the reload button, please don't repeatedly execute these functions in a
quick-fire fashion.

Basically, don't be an idiot. Thanks!

## Usage

There are basically two things cranq can do for you. You can view the incoming
queue or you can search for a package within the queue.

To show all packages in the incoming queue:

```{r}
library(cranq)
incoming()
```

To show a specific incoming stage by name:

```{r}
incoming("newbies")
```

To find a specific package within all the queues:

```{r}
check_package("musclesyneRgies")
```

Edgar Ruiz and Hadley Wickham performed some
[analysis of what these stages might mean](https://github.com/edgararuiz-zz/cran-stages).

## License

Released under the [MIT License](LICENSE.md).

Copyright (c) 2022 Mark Sellors.
